\section{System Architecture and Data Collection}
\label{sec:architecture}

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
      node distance=0.42cm,
      every node/.style={flowbox}
    ]
    \node (bws) {Binance WS};
    \node[below=of bws] (tick) {Tick Stream\\Collector};
    \node[below=of tick] (sync) {Timestamp\\Synchronizer};
    \node[below=of sync] (feat) {Feature Generator};
    \node[below=of feat] (ml) {ML / Signal Engine};
    \node[below=of ml] (bt) {Backtester};
    \node[below=of bt] (eval) {Evaluation};

    \node[right=2.4cm of sync, minimum width=2.2cm] (pws) {Polymarket WS};
    \node[below=of pws] (book) {Order Book\\Collector};

    \draw[flowarr] (bws) -- (tick);
    \draw[flowarr] (tick) -- (sync);
    \draw[flowarr] (sync) -- (feat);
    \draw[flowarr] (feat) -- (ml);
    \draw[flowarr] (ml) -- (bt);
    \draw[flowarr] (bt) -- (eval);
    \draw[flowarr] (pws) -- (book);
    \draw[flowarr] (book.west) -- (sync.east);
  \end{tikzpicture}
  \caption{OpenMarket pipeline. Binance and Polymarket WebSocket streams feed
    collectors; the recorder synchronizes events and exports aligned tables for
    feature generation, signals, and backtesting.}
  \label{fig:architecture}
\end{figure}

The codebase is a Rust workspace spanning exchange collectors, a multi-market
recorder with lag-pairing export, signal and execution engines, backtesting, and
Parquet-native ML crates (\texttt{step3-parquet-export},
\texttt{binary-outcome-trainer}); Figure~\ref{fig:architecture} shows how the
two WebSocket streams converge on the synchronizer and downstream stages.
Crate-level detail is maintained in the repository; the paper's benchmark
claims are regenerated from the frozen dataset and model artifacts, not from
live operational services.

\subsection{Binance}
\label{sec:data-binance}

The Binance collector records BTC/USDT trades and derives candle tables at
multiple time resolutions. The source schema includes trade ID, trade timestamp,
price, quantity, quote volume, maker/taker direction, and local receive time.
Millisecond-level tick snapshots preserve both source and ingest timestamps.

\subsection{Polymarket}
\label{sec:data-polymarket}

The Polymarket collector subscribes to BTC binary market order book updates,
trades, and last-trade-price events. The recorder maps token IDs to market slugs
and side labels using market metadata so that UP and DOWN books can be analyzed
consistently across rolling 15-minute markets.

\subsection{Storage}
\label{sec:data-storage}

The initial recorder stores data in SQLite for operational simplicity. The
public dataset release exports raw and processed tables to partitioned Parquet.
Key recorded tables include:
\begin{itemize}
  \item \texttt{binance\_trades}, \texttt{binance\_ticks\_ms}
  \item \texttt{polymarket\_ticks\_ms}, \texttt{market\_meta}
  \item \texttt{lag\_pairs\_ms}
  \item \texttt{binance\_candles\_1s}, \texttt{binance\_candles\_5s},
        \texttt{binance\_candles\_1m}, \texttt{binance\_candles\_5m},
        \texttt{binance\_candles\_15m}, \texttt{binance\_candles\_1h}
\end{itemize}
