\section{Dataset}
\label{sec:dataset}

The public dataset is hosted on Hugging Face:
\url{https://huggingface.co/datasets/gregyoung14/openmarket-btc-polymarket}.

\subsection{Release Status}
\label{sec:dataset-status}

The frozen release has three dataset splits and two model artifacts: unified
\texttt{v0.4.3-unified} (the deduplicated analytic split), full
\texttt{v0.2-full} (per-snapshot archive), sample \texttt{v0.1-sample}
(quickstart), model \texttt{v0.2.1/} (canonical walk-forward logistic + Platt),
and model \texttt{v0.1/} (pilot comparison). The feature demo split is not a
full feature archive; full step3 features are reproducible from unified Parquet.
Hugging Face's indexed/default dataset view may surface a larger aggregate row
count because it includes non-unified demo and full-archive artifacts; the
\OpenMarketTotalRows{} headline in this paper refers only to the deduplicated
\texttt{unified/} split.

The operator archive inventories \OpenMarketSnapshots{} CDN SQLite snapshots
published \OpenMarketCollectionStart{}--\OpenMarketCollectionEnd{}. The event
data inside those snapshots covers \OpenMarketPolyObservedDays{} observed
Polymarket days between \OpenMarketDataFirstDay{} and \OpenMarketDataLastDay{};
later snapshots are archival checkpoints of the same recorder state and add no
new event days (Section~\ref{sec:exp-scale}). Five formerly-partial
exports were recovered with \texttt{sqlite3 .recover} and re-exported before
the final unified rebuild; queue metadata reports 202~\texttt{published-clean},
0~\texttt{published-partial}, and 0~\texttt{corrupt}.

The unified split merges overlapping \texttt{full/} exports with
\path{scripts/datasets/merge_partitions.py}, removing ${\sim}$21\% duplicate
rows. This duplicate rate is expected: each \texttt{full/} snapshot is a
point-in-time export of recorder state, so adjacent snapshots intentionally
overlap in historical rows. New snapshots were published as archival checkpoints
of the current recorder database for reproducibility and recovery, rather than
as append-only deltas; this preserves independently valid per-snapshot exports
at the cost of duplicate historical rows in the raw union. The unified split
deduplicates those overlapping exports by table-specific keys and timestamps
rather than treating them as new events. All splits are validated with
\path{scripts/hf/validate_sample_split.py}. Empirical statistics are regenerated
from on-disk Parquet via \texttt{analyze\_unified.py} (Section~\ref{sec:reproducibility}).

Core table schemas are documented in the repository. Processed step3 features
for ML are exported from unified Parquet (\path{step3-parquet-export}) rather
than shipped as a full Hugging Face split.
