\section{Discussion}
\label{sec:discussion}

\subsection{What This Enables That Prior Work Does Not}

Dubach~\cite{dubach2026anatomy} establishes Polymarket microstructure stylized
facts on tick data; Saguillo et al.~\cite{saguillo2025arbitrage} quantify
arbitrage gaps. Neither provides a reproducible \textbf{Binance--Polymarket}
timeline with published pairing metadata and walk-forward calibration baselines.
OpenMarket lowers the cost of questions such as:
\begin{itemize}
  \item How stable is lead--lag across volatility/disagreement regimes?
  \item Does Polymarket mid probability subsume external drift signals?
  \item How sensitive are calibration metrics to fees, spreads, and pairing
        window~$W$?
\end{itemize}
Section~\ref{sec:insights} gives initial answers; the tooling is the enduring
contribution.

\subsection{Artifact Scope}

This work is best read as a \textbf{data-and-methods} release with empirical
baselines. Its primary claim is reproducible public infrastructure: a
synchronized corpus, pairing metadata, validation commands, and baseline
diagnostics that make future microstructure and forecasting comparisons easier
to audit. Its primary empirical result is negative: on this corpus, a
walk-forward multivariate model does not beat the market's own mid
out-of-sample, and simulated trading is cost-dominated.

\subsection{Domain Generalizability}

BTC 15-minute markets are a high-activity microcosm of Polymarket CLOB trading:
useful for synchronization methodology and short-horizon forecasting baselines,
but not representative of slower political or macro markets. Extensions to other
assets should preserve source/ingest timestamps and publish pairing metadata the
way this release does.

\subsection{Operational and Regulatory Context}

Polygon settlement latency, oracle definition risk, and U.S.\ regulatory
uncertainty affect economic interpretation but are outside our artifact. We
document clock-offset diagnostics and WebSocket gaps; users should not treat
top-of-book backtests as executable PnL without explicit queue and fee models.

\subsection{Data Availability and Ethics}
\label{sec:release}

The public release comprises the GitHub repository
(\url{https://github.com/gregyoung14/openmarket}, tag \OpenMarketReleaseTag{},
Apache~2.0), the Hugging Face dataset
\texttt{gregyoung14/openmarket-btc-polymarket} (\texttt{v0.4.3-unified},
\texttt{v0.2-full}, \texttt{v0.1-sample}) and models
\texttt{gregyoung14/openmarket-models} (\texttt{v0.2.1/}, \texttt{v0.1/}),
mdBook and Rust API documentation, a Jupyter quickstart
(\path{notebooks/quickstart.ipynb}), Docker reproducibility scaffolding, a
citation guide (\path{CITATION.md}), and the sanitized operational archive
(\path{research/operational/}).
The frozen source tag \OpenMarketReleaseTag{} resolves to commit
\path{f609d4dd6057a00e1bc94c220331e0495796ebf3}; this paper build was
generated from commit \path{223692dc46e2cc8f47d3c8122767b1dc420428f2}. The
archive inventory contains \OpenMarketSnapshots{} snapshots
(46.21~GB compressed), and the generated characterization manifest is shipped
as \path{paper/assets/stats/characterization.json}. A DOI/Zenodo record has not
yet been assigned; derivative work should cite the Hugging Face dataset/model
revision hashes and the frozen source tag.
The corpus contains only public market data (order books, trades,
metadata) collected from open APIs---no user identities or private positions.
Dataset and model cards document licenses and version pins. Cite the dataset
version and source tag (\OpenMarketReleaseTag{}) in derivative work.

\subsection{Archive Status and Extensions}
\label{sec:future-work}

OpenMarket completed archival closeout on 2026-07-01. Active data collection
and model maintenance have ended; source tag \OpenMarketReleaseTag{} freezes
the public research record. Community extensions that the frozen artifacts
support include additional exchanges and assets, Polymarket non-crypto
markets, multi-vantage collection to resolve the constant clock-offset
component (Section~\ref{sec:sync-clock}), richer order-book reconstruction,
stronger model baselines (tree ensembles, neural sequence models), improved
execution simulation, and a public benchmark leaderboard---none of which
imply ongoing maintenance.
