\section{Limitations}
\label{sec:limitations}

\textbf{Domain scope.} BTC 15-minute Polymarket binaries are a niche but liquid
regime: high tick rate, tight spreads, and volatile underlying spot. Stylized
facts and benchmarks here may not transfer to election markets, long-dated
events, or illiquid books without re-collection and re-calibration. In
particular, political and macro markets often have lower tick rates, wider and
more intermittent books, discrete news shocks, ambiguous or delayed settlement
mechanics, and no single liquid external reference stream analogous to
BTC/USDT. Those differences can break both the synchronization assumptions
(dense cross-venue observations inside millisecond windows) and the forecasting
features calibrated for short-horizon crypto price discovery.

\textbf{Data and methods.} WebSocket outages can create gaps; relative venue
clock drift is bounded empirically
(${\leq}\OpenMarketDriftBound{}$~ms, Section~\ref{sec:sync-clock}) but
source-clock lead--lag retains a roughly
$\pm\OpenMarketEnvBinanceMed{}$~ms constant-offset ambiguity from a single
collection vantage point; resolving that component would require
multi-vantage collection; top-of-book backtests may overstate execution
quality; mishandled
settlement labels can leak information; and step3 export covers 2{,}251 of
4{,}450 \texttt{market\_meta} markets for the reasons audited in
Section~\ref{sec:ml}. Full-archive \texttt{features/} Parquet is not on
Hugging Face (run \path{export_step3_from_parquet} locally).

\textbf{Model comparisons.} The repository contains legacy XGBoost, LightGBM,
stacking, and SHAP prototypes, but these were exploratory strategy artifacts,
not frozen benchmarks on the unified \texttt{v0.4.3} step3 export. The main
paper therefore reports only baselines regenerated from the archived release.
Direct tree-model, neural sequence, and market-by-market benchmark suites remain
future work.

\textbf{Live trading.} Simulated outcomes are sensitive to regime and fee
assumptions; live execution adds latency, queue position, partial fills, and
regulatory uncertainty not modeled in this artifact. The operational archive is
included only as sanitized audit context; it is not a recommendation to run live
trading infrastructure and should not be interpreted as a profitability claim.
