\section{Features and Machine Learning}
\label{sec:ml}

Feature families include order-book metrics (spread, best bid/ask, microprice,
imbalance, depth, book update velocity), price metrics (returns, realized
volatility, momentum, VWAP deviation, candle shape), technical indicators, and
custom short-horizon signals derived from aligned ticks. Features are paired
with settlement labels downstream. The repository also preserves exploratory
strategy and model prototypes, but the \textbf{published} binary-outcome model
uses a Rust pipeline on unified Parquet:

\begin{enumerate}
  \item \texttt{export\_step3\_from\_parquet} reads \texttt{v0.4.3-unified}
        tables and emits step3 calibration CSVs (43 features).
  \item \texttt{train\_binary\_outcome\_model} performs walk-forward logistic
        regression by market, applies Platt scaling~\cite{platt1999probabilistic},
        and writes JSON artifacts.
\end{enumerate}
The Polymarket mid prior used as the naive baseline is sampled at the same
feature-cutoff timestamp as the model inputs, so the comparison uses identical
information timing. Within each walk-forward window, both the logistic model
and Platt calibrator are fit only on pre-cutoff training/calibration rows;
scored OOS rows are not used for fitting or calibration.

On the publication workstation (Apple M5 Max), step3 export of 357{,}390 rows
across 2{,}251 markets completes in ${\sim}$63\,s; training (559 walk-forward
windows) completes in ${\sim}$67\,s. Step3 export writes 51\% of
\texttt{market\_meta} markets. The coverage audit over 4{,}450 markets reports
2{,}251 written, 1{,}241 with no Polymarket ticks in the export window, 922
with insufficient Binance trades for signal construction, 21 with missing
Binance partitions, 14 with no valid order-book snapshots after feature filters,
and one tied BTC close that is dropped because the binary label is undefined.

For public releases, model binaries are uploaded to Hugging Face Models rather
than committed to Git. The canonical \texttt{v0.2.1/} benchmark is the pooled
walk-forward OOS result across 559 windows: AUC \OpenMarketModelOosAuc{},
Brier \OpenMarketModelOosBrier{}, and ECE \OpenMarketModelOosEce{}. The same
rows give the naive mid prior AUC \OpenMarketNaiveOosAuc{}, Brier
\OpenMarketNaiveOosBrier{}, and ECE \OpenMarketNaiveOosEce{}, so the model
slightly underperforms the market prior. The frozen exported scorer evaluated on
the full 357{,}390-row step3 timeline is retained only as a diagnostic
reproducibility number because it includes each window's training rows
(Section~\ref{sec:insights-forecast}).
Simulated positive-EV trading under 1\% fees and 0.5\% slippage yields
$-0.116$ normalized payoff units per attempted trade. In the simulator, a
losing trade loses one staked unit plus fee, while a winning trade earns the
contract payoff net of entry price, fee, and slippage. An earlier
\texttt{v0.1/} pilot artifact remains for comparison.
Reliability and per-window metrics are regenerated by
\texttt{generate\_ml\_figures.py}; forecast ablations against naive baselines
are in Section~\ref{sec:insights-forecast}.
