\section{Related Work}
\label{sec:related-work}

Prediction markets aggregate dispersed information into tradable prices
\cite{wolfers2004prediction,hanson2003combinatorial,berg2008prediction}.
The broader prediction-market literature studies forecast accuracy, incentive
compatibility, and event-study use cases, while market-microstructure research
studies how order flow, liquidity, latency, and price impact determine
short-horizon prices \cite{madhavan2000survey,ohara2015high,cont2014price}.
OpenMarket sits at the intersection: it treats a prediction market as a
high-frequency limit-order-book venue whose prices are probabilities.

\textbf{Public high-frequency order-book datasets.}
LOBSTER~\cite{huang2011lobster} reconstructs NASDAQ limit-order books for
academic use, and FI-2010~\cite{ntakaris2018benchmark} is a widely used
mid-price forecasting benchmark. The limit-order-book survey literature
\cite{gould2013limit} and neural LOB forecasting work such as
DeepLOB~\cite{zhang2019deeplob} show why public, timestamped order-book
benchmarks matter: they enable method comparison under fixed reconstruction and
evaluation rules. These datasets and models cover traditional equity venues.
OpenMarket follows this lineage but targets a decentralized prediction-market
CLOB paired with a crypto spot reference stream, settlement labels, and explicit
cross-venue pairing metadata.

\textbf{Polymarket and decentralized prediction-market data.}
Dubach~\cite{dubach2026anatomy} analyzes tick-level Polymarket order-book
evidence and releases analysis code, but does not ship a synchronized Binance
reference stream or a Hugging Face archival corpus. Saguillo et
al.~\cite{saguillo2025arbitrage} document combinatorial arbitrage and market
replications using proprietary-scale scrapes; reproduction requires
re-implementing data collection. Rahman et al.~\cite{rahman2025sok} survey DePM
design trade-offs without a cross-venue BTC 15-minute benchmark.
Recent Polymarket dataset releases are complementary rather than substitutes.
PolyBench~\cite{cheng2026polybench} provides timestamp-locked Polymarket order
book and news snapshots for LLM forecasting and trading evaluation. Jia et
al.~\cite{jia2026forecasting} construct a full-lifecycle Polymarket dataset
suite spanning market metadata, fill-level trading records, and oracle
resolution events. Qin and Yang~\cite{qin2026polymarketv1} release a complete
on-chain first-generation Polymarket archive with ground-truth aggressor
direction. OpenMarket differs by focusing narrowly on millisecond-level BTC
15-minute CLOB dynamics paired with Binance BTC/USDT and by publishing explicit
\texttt{lag\_pairs\_ms} construction metadata.

\textbf{Crypto price discovery and cross-venue timing.}
Multi-venue studies measure which market contributes to price discovery
\cite{hasbrouck1995one}. In crypto, Brandvold et
al.~\cite{brandvold2015bitcoin} estimate information shares across Bitcoin
exchanges, and Makarov and Schoar~\cite{makarov2020trading} document
cross-exchange crypto arbitrage and segmentation at scale. Public Binance kline
and trade products support many such studies, but they do not include
Polymarket CLOB state, settlement labels, or prediction-market-specific pairing
metadata. OpenMarket therefore does not claim to improve crypto price-discovery
estimation in general; it supplies a reproducible cross-venue corpus for a
specific prediction-market mechanism.

\textbf{Clock synchronization and timestamp validity.}
High-frequency cross-venue inference depends on timestamp semantics. NTPv4
specifies Internet clock synchronization against UTC~\cite{mills2010ntp};
precision-time deployments use IEEE 1588/PTP for tighter synchronization
\cite{ieee1588}. Financial regulation also treats clock accuracy as a
surveillance requirement: MiFID II RTS 25 specifies maximum UTC divergence and
timestamp granularity for trading venues and participants
\cite{mifid2016rts25}. OpenMarket is not a regulated trading venue and uses a
single public collector, so it cannot identify absolute venue-clock offsets
without additional vantage points. Its contribution is to publish both
source and ingest timestamps and to quantify which timing claims survive that
limitation.

\textbf{Open infrastructure.}
Most open-source trading repositories mix notebooks, private snapshots, and
undocumented assumptions. OpenMarket differs by publishing (i) raw and deduped
Parquet splits, (ii) explicit \texttt{lag\_pairs\_ms} with quality flags, (iii)
Rust exporters/trainers with pinned commands, and (iv) empirical baselines on the
released corpus.

We claim infrastructure and reproducible characterization, not superior live
trading performance. Dubach provides a deeper single-venue microstructure
analysis, while Saguillo et al. study broader proprietary-scale arbitrage data
than this public BTC 15-minute release.
