\section{Introduction}
\label{sec:introduction}

OpenMarket began as a trading system, not a dataset. We built a Rust
pipeline to trade Polymarket's BTC 15-minute binary markets against Binance
BTC/USDT spot flow: WebSocket collectors for both venues, a millisecond
recorder, a walk-forward calibrated logistic scorer, and simulated and paper
execution. The result was negative. No strategy iteration survived fees and
spread; out-of-sample, the strongest published model \emph{does not beat, and
slightly underperforms} the probability already implied by Polymarket's own
order book (Section~\ref{sec:insights-forecast}); and simulated positive-EV
trading nets $-0.116$ normalized payoff units per attempted trade under stated
fee and slippage assumptions. We do not claim trading profitability---the
central empirical finding is the opposite, and that negative result is
published with the data that produced it.

This paper releases the resulting infrastructure and corpus, which outlived
the trading strategy. Empirical work now documents tick-level
Polymarket dynamics, decentralized prediction-market (DePM) design
trade-offs, and combinatorial arbitrage
\cite{dubach2026anatomy,saguillo2025arbitrage,rahman2025sok}. What remains
missing is a \textbf{public, cross-venue, millisecond-resolution corpus}
paired with Binance BTC/USDT and tooling that makes synchronization
quality, lead--lag, and calibration analysis reproducible at archival
scale. OpenMarket closes that gap. The contribution is threefold:
\begin{enumerate}
  \item \textbf{Corpus.} To our knowledge, the first public millisecond-level
        Polymarket BTC / Binance BTC-USDT paired corpus with explicit pairing
        metadata: \OpenMarketTotalRows{} deduplicated rows across
        \OpenMarketSnapshots{} archival snapshots, with event data on
        \OpenMarketPolyObservedDays{} observed days
        (\OpenMarketDataFirstDay{}--\OpenMarketDataLastDay{};
        Section~\ref{sec:exp-scale}), including
        \OpenMarketLagPairs{} explicit lead--lag pairs.
  \item \textbf{Methods.} Documented source-vs.-ingest synchronization
        with empirical clock-offset validation
        (Section~\ref{sec:sync-clock}), Parquet-native export,
        walk-forward calibration training, and validation harnesses that
        treat clock drift and pairing-window sensitivity as measurable
        objects rather than implementation details.
  \item \textbf{Empirical baselines.} Stylized facts and forecast
        benchmarks on the released corpus---top-of-book spreads, lead--lag
        distributions, and ablations testing whether multivariate models
        outperform naive order-book mid priors (out-of-sample, they do
        not).
\end{enumerate}

The initial empirical claims are intentionally narrow:
\begin{enumerate}
  \item BTC 15-minute top-of-book spreads are usually one tick wide.
  \item Source-clock lead--lag has a compact median but heavy tails.
  \item Polymarket quotes respond to large Binance moves after hundreds of
        milliseconds on the collector clock.
  \item Lead--lag timing changes little across cross-venue disagreement regimes.
  \item Multivariate features slightly underperform the Polymarket mid prior
        out-of-sample.
\end{enumerate}

The released artifacts deliberately include the full research trail: the
collectors and recorder, the synchronization layer, the feature and
training pipelines, the backtesting framework, the strategy-evolution archive,
the Hugging Face dataset and model releases, and a sanitized operational
appendix for audit context. OpenMarket is frozen as a public research archive
(source tag \OpenMarketReleaseTag{}); active collection has ended. The remainder of the
paper describes the system, the released artifacts, and initial microstructure
findings that prior single-venue or closed pipelines cannot support.
