\section{Features and Machine Learning}
\label{sec:ml}

Feature families include order-book metrics (spread, best bid/ask, microprice,
imbalance, depth, book update velocity), price metrics (returns, realized
volatility, momentum, VWAP deviation, candle shape), technical indicators (RSI,
EMA, VWAP, ATR, Bollinger Bands, MACD, ADX), and custom signals (drift score,
order-flow acceleration, scoreboard signal, whipsaw/chop detector, volume gate,
Brier calibration monitor, confidence-bin empirical edge). Features are
computed from aligned ticks and paired with settlement labels downstream.

The project includes historical Python prototypes and Rust signal code. The
legacy ML archive includes XGBoost, LightGBM, logistic meta-classifiers, SHAP
feature analysis, and stacked ensembles. The \textbf{published} binary-outcome
model uses a Rust pipeline on unified Parquet:

\begin{enumerate}
  \item \texttt{export\_step3\_from\_parquet} reads \texttt{v0.4.3-unified}
        tables and emits step3 calibration CSVs (43 features).
  \item \texttt{train\_binary\_outcome\_model} performs walk-forward logistic
        regression by market, applies Platt scaling~\cite{platt1999probabilistic},
        and writes JSON artifacts.
\end{enumerate}

On the publication workstation (Apple M5 Max), step3 export of 357{,}390 rows
across 2{,}251 markets completes in ${\sim}$63\,s; training (559 walk-forward
windows) completes in ${\sim}$67\,s. Step3 export writes 51\% of
\texttt{market\_meta} markets. The coverage audit over 4{,}450 markets reports
2{,}251 written, 1{,}241 with no Polymarket ticks in the export window, 922
with insufficient Binance trades for signal construction, 21 with missing
Binance partitions, 14 with no valid order-book snapshots after feature filters,
and one tied BTC close that is dropped because the binary label is undefined.

For public releases, model binaries are uploaded to Hugging Face Models rather
than committed to Git. The canonical \texttt{v0.2.1/} benchmark is the frozen
exported scorer evaluated on the full 357{,}390-row step3 timeline: AUC 0.841,
Brier 0.163, and ECE 0.027 (Section~\ref{sec:insights-forecast}). Because the
full timeline includes each window's training rows, this figure is an
optimistic bound; the training artifact also records the walk-forward
diagnostic (pooled OOS AUC \OpenMarketModelOosAuc{},
Brier \OpenMarketModelOosBrier{}, ECE 0.025 across 559 windows), and
Section~\ref{sec:insights-forecast} compares both against the naive mid prior
on the same rows.
Simulated positive-EV trading under 1\% fees and 0.5\% slippage yields
$-0.117$ PnL per trade. An earlier \texttt{v0.1/} pilot artifact remains for
comparison.
Reliability and per-window metrics are regenerated by
\texttt{generate\_ml\_figures.py}; forecast ablations against naive baselines
are in Section~\ref{sec:insights-forecast}.
