\section{Related Work}
\label{sec:related-work}

Prediction markets aggregate dispersed information into tradable prices
\cite{wolfers2004prediction,hanson2003combinatorial,berg2008prediction}.
High-frequency microstructure methods emphasize order-book dynamics, latency,
and price impact \cite{ohara2015high,cont2014price}. Multi-venue studies
measure which market contributes to price discovery \cite{hasbrouck1995one}.

\textbf{Polymarket microstructure.}
Dubach~\cite{dubach2026anatomy} analyzes tick-level Polymarket order-book
evidence and releases analysis code, but does not ship a synchronized Binance
reference stream or a Hugging Face archival corpus. Saguillo et al.~\cite{saguillo2025arbitrage}
document combinatorial arbitrage and market replications using proprietary-scale
scrapes; reproduction requires re-implementing data collection. Rahman et al.~\cite{rahman2025sok}
survey DePM design trade-offs without a cross-venue BTC 15-minute benchmark.

\textbf{Crypto spot data.}
Public Binance kline and aggTrade products are widely used, but they do not
include Polymarket CLOB state, settlement labels, or pairing metadata needed for
prediction-market forecasting studies.

\textbf{Open infrastructure.}
Most open-source trading repositories mix notebooks, private snapshots, and
undocumented assumptions. OpenMarket differs by publishing (i) raw and deduped
Parquet splits, (ii) explicit \texttt{lag\_pairs\_ms} with quality flags, (iii)
Rust exporters/trainers with pinned commands, and (iv) empirical baselines on the
released corpus.

Table~\ref{tab:related-work} summarizes positioning. We claim infrastructure
and reproducible characterization, not superior live trading performance.

\begin{table}[t]
  \centering
  \caption{Comparison with adjacent artifacts (tick-level PM focus).}
  \label{tab:related-work}
  \footnotesize
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{@{}lccccc@{}}
    \toprule
    Artifact & PM ticks & Binance ref. & HF corpus & Cross-venue pairs & OSS repro \\
    \midrule
    Dubach (2026)~\cite{dubach2026anatomy} & \checkmark & -- & partial & -- & \checkmark \\
    Saguillo (2025)~\cite{saguillo2025arbitrage} & \checkmark & -- & -- & -- & partial \\
    Public Binance dumps & -- & \checkmark & \checkmark & -- & \checkmark \\
    OpenMarket (this work) & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    \bottomrule
  \end{tabular}
\end{table}